\clearpage

# TABLES

```{r tab-catch-5abcd}
catch.table(catch.5,
            catch.5.discards,
            area = "5ABCD",
 cap = paste0("Reported catch (mt) of Pacific Cod in Area 5ABCD ",
              "by Canada and the USA, ",
              min(catch.5$year), "--", max(catch.5$year),
              ". The reported discards for the period ", min(catch.5$year),
              "--1995 are ",
              "unrepresentative of true discarding because the estimates were taken ",
              "from logbooks. Discard estimates since 1996 are based on at-sea ",
              "observations and are considered to be more representative of true discarding."))

```

\clearpage

```{r tab-catch-3cd}
catch.table(catch.3,
            catch.3.discards,
            area = "3CD",
 cap = paste0("Reported catch (mt) of Pacific Cod in Area 3CD ",
              "by Canada and the USA, ",
              min(catch.3$year), "--", max(catch.3$year),
              ". The reported discards for the period ", min(catch.3$year),
              "--1995 are ",
              "unrepresentative of true discarding because the estimates were taken ",
              "from logbooks. Discard estimates since 1996 are based on at-sea ",
              "observations and are considered to be more representative of true discarding."))
```

\clearpage

```{r tab-tac}
tac.table(tac,
 cap = paste0("Summary of TACs by area."))
```

\clearpage

```{r tab-priors-5abcd}
# priors.table(base.model.5abcd,
# basis.vec = c("Noninformative",
#               "Informative-Previous assessment",
#               "Informative-Previous assessment",
#               "No prior-Fixed parameter",
#               "No prior-Fixed parameter",
#               "No prior-Fixed parameter",
#               "No prior-Fixed parameter",
#               "Noninformative-Technical necessity",
#               "Noninformative-Technical necessity",
#               "Noninformative-Technical necessity",
#               "Noninformative-Technical necessity",
#               "Noninformative-Technical necessity"),
#              cap = paste0("Prior probability distributions, their parameters and initial values used in the ",
#                           "Area 5ABCD Reference Case model. ", q.5abcd.desc))
```

\clearpage

```{r tab-priors-3cd}
# priors.table(base.model.3cd,
# basis.vec = c("Noninformative",
#               "Informative-Previous assessment",
#               "Informative-Previous assessment",
#               "No prior-Fixed parameter",
#               "No prior-Fixed parameter",
#               "No prior-Fixed parameter",
#               "No prior-Fixed parameter",
#               "Noninformative-Technical necessity",
#               "Noninformative-Technical necessity",
#               "Noninformative-Technical necessity",
#               "Noninformative-Technical necessity"),
#              cap = paste0("Prior probability distributions, their parameters and initial values used in the ",
#                           "Area 3CD Reference Case model. ", q.3cd.desc))
```

```{r tab-suggested-ref-points}
suggested.ref.points()
```

\clearpage

## MODEL RESULTS: AREA 5ABCD

```{r tab-param-table-5abcd, results='asis'}
# make.parameters.table(base.model.5abcd,
#   caption = paste0("Estimated and fixed parameters and prior probablilty distributions used ",
#     "in the Reference Case, Area 5ABCD."),
#   omit_pars = c("Log initial recruitment ($\\ln(\\overline{R}_{init})$)",
#     "Log mean recruitment ($\\ln(\\overline{R})$)"),
#   omit_selectivity_pars = TRUE)
```

```{r tab-param-est-table-5abcd, results='asis'}
# pars_est_omit <- c("$\\overline{R}_{init}$", "$\\overline{R}$", "$\\vartheta$")
# make.parameters.est.table(base.model.5abcd,
#   caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
#     "97.5\\textsuperscript{th} percentile) and MPD ",
#     "estimates of key parameters from the Reference Case, Area 5ABCD. $R_0$ is in thousands of fish. $B_0$ is in tonnes. ",
#     q.5abcd.desc),
#   omit_pars = pars_est_omit)
```

```{r tab-ref-points-table-5abcd, results='asis'}
# make.ref.points.table(base.model.5abcd,
#                       omit_msy = TRUE,
#                       add.hist.ref = TRUE,
#                       lrp = c(2000, 2000),
#                       usr = c(1956, 2004),
#                       digits = 2,
#                       caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
#                                        "97.5\\textsuperscript{th} percentile) of reference points for Area 5ABCD. ",
#                                        "Biomass is in tonnes."))
```

```{r tab-post-biomass-5abcd, results='asis'}
# make.value.table(base.model.5abcd,
#                  1,
#                  digits = 0,
#                  caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
#                                   "percentile) and MPD estimates of biomass (t) for the Reference Case, ",
#                                   "Area 5ABCD."))
```

\clearpage

```{r tab-post-depl-5abcd}
# make.value.table(base.model.5abcd,
#                  5,
#                  digits = 2,
#                  caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
#                                   "percentile) and MPD estimates of biomass relative to $B_0$ ",
#                                   "for the Reference Case, Area 5ABCD."))
```

\clearpage

```{r tab-post-recr-5abcd, results='asis'}
# make.value.table(base.model.5abcd,
#                  2,
#                  digits = 0,
#                  caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
#                                   "percentile) and MPD estimates of recruitment (thousands) for the Reference Case, ",
#                                   "Area 5ABCD."))
```

\clearpage

```{r tab-post-f-5abcd, results='asis'}
# make.value.table(base.model.5abcd,
#                  3,
#                  digits = 2,
#                  caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
#                                   "percentile) and MPD estimates of fishing mortality, F, ",
#                                   "for the Reference Case, Area 5ABCD."))
```

\clearpage

## MODEL RESULTS: AREA 3CD

```{r tab-param-table-3cd, results='asis'}
# make.parameters.table(base.model.3cd,
#   caption = paste0("Estimated and fixed parameters and prior probablilty distributions used ",
#     "in the Reference Case, Area 3CD."),
#   omit_pars = c("Log initial recruitment ($\\ln(\\overline{R}_{init})$)",
#     "Log mean recruitment ($\\ln(\\overline{R})$)"),
#   omit_selectivity_pars = TRUE)
```

```{r tab-param-est-table-3cd, results='asis'}
# make.parameters.est.table(base.model.3cd,
#   caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
#     "97.5\\textsuperscript{th} percentile) and MPD ",
#     "estimates of key parameters from the reference Case, Area 3CD. $R_0$ is in thousands of fish. $B_0$ is in tonnes.  ",
#     q.5abcd.desc),
#   omit_pars = pars_est_omit)
```

```{r tab-ref-points-table-3cd, results='asis'}
# make.ref.points.table(base.model.3cd,
#                       omit_msy = TRUE,
#                       add.hist.ref = TRUE,
#                       lrp = c(1986, 1986),
#                       usr = c(1956, 2004),
#                       digits = 2,
#                       caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
#                                        "97.5\\textsuperscript{th} percentile) of reference points for Area 3CD. ",
#                                        "Biomass is in tonnes."))
```

```{r tab-post-biomass-3cd, results='asis'}
# make.value.table(base.model.3cd,
#                  1,
#                  digits = 0,
#                  caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
#                                   "percentile) and MPD estimates of biomass (t) for ",
#                                   "the Reference Case, Area 3CD."))
```

\clearpage

```{r tab-post-depl-3cd}
# make.value.table(base.model.3cd,
#                  5,
#                  digits = 2,
#                  caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
#                                   "percentile) and MPD estimates of biomass relative to $B_0$ ",
#                                   "for the Reference Case, Area 3CD."))
```

\clearpage

```{r tab-post-recr-3cd, results='asis'}
# make.value.table(base.model.3cd,
#                  2,
#                  digits = 0,
#                  caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
#                                   "percentile) and MPD estimates of recruitment (thousands) for the Reference Case,",
#                                   "Area 3CD."))
```

\clearpage

```{r tab-post-f-3cd, results='asis'}
# make.value.table(base.model.3cd,
#                  3,
#                  digits = 2,
#                  caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
#                                   "percentile) and MPD estimates of fishing mortality, F, ",
#                                   "for the Reference Case, Area 3CD."))
```

\clearpage

## SELECTED SENSITIVITY RESULTS

*Copy Sensitivity chunks from 2018 Rmd file if needed*


\clearpage

## MODEL-AVERAGED REFERENCE POINTS AND DECISION TABLES {#sec:reference-points-and-decision-tables}


```{r tab-ref-points-table-avg-5abcd, results='asis'}
# make.ref.points.table(c(base.model.5abcd,
#                         sens.models.6.sub),
#                       omit_msy = TRUE,
#                       add.hist.ref = TRUE,
#                       lrp = c(2000, 2000),
#                       usr = c(1956, 2004),
#                       digits = 2,
#                       caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
#                                        "97.5\\textsuperscript{th} percentile) of reference points for ",
#                                        "model-averaged Area 5ABCD. ",
#                                        "Biomass is in tonnes."))
```

```{r tab-post-biomass-avg-5abcd, results='asis'}
# make.value.table(c(base.model.5abcd,
#                         sens.models.6.sub),
#                  1,
#                  digits = 0,
#                  caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
#                                   "percentile) and MPD estimates of biomass (t) for model-averaged Area 5ABCD."))
```

```{r tab-post-recr-avg-5abcd, results='asis'}
# make.value.table(c(base.model.5abcd,
#                         sens.models.6.sub),
#                  2,
#                  digits = 0,
#                  caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
#                                   "percentile) and MPD estimates of recruitment (thousands) model-averaged Area 5ABCD."))
```

```{r tab-ref-points-table-avg-3cd, results='asis'}
# make.ref.points.table(c(base.model.3cd,
#                         sens.models.13.sub),
#                       omit_msy = TRUE,
#                       add.hist.ref = TRUE,
#                       lrp = c(1986, 1986),
#                       usr = c(1956, 2004),
#                       digits = 2,
#                       caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and ",
#                                        "97.5\\textsuperscript{th} percentile) of reference points for ",
#                                        "model-averaged Area 3CD. ",
#                                        "Biomass is in tonnes."))
```
\vspace{10pt}
```{r tab-post-biomass-avg-3cd, results='asis'}
# make.value.table(c(base.model.3cd,
#                         sens.models.13.sub),
#                  1,
#                  digits = 0,
#                  caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
#                                   "percentile) and MPD estimates of biomass (t) for model-averaged Area 3CD."))
```

```{r tab-post-recr-avg-3cd, results='asis'}
# make.value.table(c(base.model.3cd,
#                         sens.models.13.sub),
#                  2,
#                  digits = 0,
#                  caption = paste0("Posterior (2.5\\textsuperscript{th} percentile, Median, and 97.5\\textsuperscript{th} ",
#                                   "percentile) and MPD estimates of recruitment (thousands) model-averaged Area 3CD."))
```



```{r tab-decision-avg-5abcd, results='asis'}
# decision.table(avg.model.5abcd,
#                caption = paste0("Decision table with model averaging for Area 5ABCD. Models averaged are: ",
#                                 and.string(c(base.model.5abcd.name, sens.models.name.6.sub)),
#                                 "."))
```


```{r tab-decision-avg-3cd, results='asis'}
# decision.table(avg.model.3cd,
#                caption = paste0("Decision table with model averaging for Area 3CD. Models averaged are: ",
#                                 and.string(c(base.model.3cd.name, sens.models.name.13.sub)),
#                                 "."))
```

\clearpage
