\clearpage

`r if(knitr:::is_latex_output()) '\\Appendices'`

`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`

# FISHERY-INDEPENDENT INDICES OF ABUNDANCE {#app:survey-appendix}

## CANADIAN SURVEYS

### HECATE STRAIT ASSEMBLAGE SURVEY

A series of multi-species groundfish bottom trawl surveys was conducted in
Hecate Strait in May-June of 1984, 1987, 1989, 1991, 1993, 1995, 1996, 1998,
2000, 2002, and 2003 @westrheim1984, @fargo1984, @fargo1988, @wilson1991,
@hand1994, @workman1996, @workman1997, @choromanski2002)  (Figure
\@ref(fig:survey-maps-hs-msa). The results up to 2000 were reported in the 2001
assessment [@sinclair2001] and results from 2002 and 2003 were presented in the
2005 assessment [@sinclair2005].

The original design of this survey assigned fishing locations by 10 fm depth
intervals within a 10 nm grid of Hecate Strait. The survey was post-stratified
for the purpose of calculating an abundance index for Pacific Cod
[@sinclair2000]. The post stratification used 10 fm depth intervals for the
entire survey area, thereby treating each depth interval as a single stratum.

The Hecate Strait Assemblage survey was designed as a systematic
fixed-station survey. Despite attempts to apply post-sampling stratification,
this approach had high survey variance [@sinclair2007]. In 2004 the Hecate
Strait Assemblage survey was discontinued in favour of the Hecate Strait
Synoptic survey (described below).

### HECATE STRAIT SYNOPTIC SURVEY

The Hecate Strait synoptic groundfish bottom trawl survey is part of
a coordinated set of long-term surveys that together cover the continental
shelf and upper slope of most of the BC coast (Figure
\@ref(fig:survey-maps-syn-hs). The Hecate Strait synoptic survey has been
conducted during May-June, in odd years since 2005. All the synoptic surveys
follow a random depth stratified design. The survey area is divided into 2 km
by 2 km blocks and each block is assigned to one of four depth strata based on
the average bottom depth in the block. The four depth strata for the Hecate
Strait survey are 10--70m, 70--130m, 130--220m, and 220--500m. Each year blocks
are randomly selected within each depth strata. For this survey and the other
synoptic surveys discussed below, the relative allocation of blocks amongst
depth strata was determined by modeling the expected catches of groundfish and
determining the target number of tows per stratum that would provide sufficiently
precise catch rate data for as many species as possible.

### QUEEN CHARLOTTE SOUND SYNOPTIC SURVEY

The Queen Charlotte Sound (QCS) synoptic groundfish bottom trawl survey has
been conducted in July--August in 2003, 2004, and in odd years since 2005
(Figure \@ref(fig:survey-maps-syn-qcs). The four depth strata for the QCS
survey are 50--125m, 125--200m, 200--330m, and 330--500 m. Each year blocks are
randomly selected within each depth strata. In addition, for the purposes of
allocating blocks, the QCS survey is divided into northern and southern spatial
strata.

### WEST COAST VANCOUVER ISLAND SYNOPTIC SURVEY

The West Coast Vancouver Island synoptic bottom trawl survey was first
conducted in 2004 and is conducted in alternating (even-numbered) years on
a chartered commercial trawler (Figure \@ref(fig:survey-maps-syn-wcvi)). The
survey area is off the west coast of Vancouver Island from approximately 49
$^\circ$  12$^\prime$ to 50 $^\circ$ 36$^\prime$ North latitude and
approximately 124 $^\circ$  48$^\prime$ to 128 $^\circ$  30$^\prime$ West
longitude. The southern boundary is contiguous with the Canada/U.S. boundary.
The survey has a single aerial stratum in Pacific Fishery Management Area
regions 3C and 3D separated into four depth strata: 50--125m; 125--200m;
200--330m; and 330--500m. Approximately 150 to 180 4 km^2^ blocks are selected
randomly among the four depth strata when conducting each survey.

```{r survey-maps-hs-msa, fig.asp=1, fig.cap="Individual survey tows for the Hecate Strait multi-species groundfish bottom trawl survey. Light gray crosses indicate survey sets that did not catch Pacific Cod. Circles have their area and color proportional to the density of Pacific Cod for that survey set. Eastings and Northings are for UTM zone 9."}
plot_multiyear_survey_sets(dat$survey_sets, "HS MSA")
```

```{r survey-maps-syn-hs, fig.asp=1, fig.cap="Individual survey tows for the Hecate Strait (SYN HS) synoptic groundfish bottom trawl survey. Light gray crosses indicate survey sets that did not catch Pacific Cod. Circles have their area and color proportional to the density of Pacific Cod for that survey set. Eastings and Northings are for UTM zone 9."}
plot_multiyear_survey_sets(dat$survey_sets, "SYN HS")
```

```{r survey-maps-syn-qcs, fig.asp=1, fig.cap="Individual survey tows for the Queen Charlotte Sound (SYN QCS) synoptic groundfish bottom trawl survey. Light gray crosses indicate survey sets that did not catch Pacific Cod. Circles have their area and color proportional to the density of Pacific Cod for that survey set. Eastings and Northings are for UTM zone 9."}
plot_multiyear_survey_sets(dat$survey_sets, "SYN QCS")
```

```{r survey-maps-syn-wcvi, fig.asp=1, fig.cap="Individual survey tows for the West Coast Vancouver Island (SYN WCVI) synoptic groundfish bottom trawl survey survey. Light gray crosses indicate survey sets that did not catch Pacific Cod. Circles have their area and color proportional to the density of Pacific Cod for that survey set. Eastings and Northings are for UTM zone 9."}
plot_multiyear_survey_sets(dat$survey_sets, "SYN WCVI")
```

\clearpage

### SWEPT AREA ANALYSIS

For all Canadian surveys, a swept area estimate of biomass in any year $y$ was
obtained by summing the product of the CPUE and the area surveyed across the
surveyed strata $i$:

\begin{equation}
  B_y = \sum_{i=1}^kC_{y_i}A_i=\sum_{i=1}^kB_{y_i}
  (\#eq:sweptareabiomass)
\end{equation}

where
$C_{y_i}$ = mean CPUE density (kg/km^2^) for Pacific Cod in stratum $i$,
$A_i$ = area of stratum $i$ (km^2^),
$B_{y_i}$ = biomass of Pacific Cod in stratum $i$ for year $y$, and
$k$ = number of strata.

CPUE ($C_{y_i}$) for Pacific Cod in stratum $i$ for year $y$ was calculated as
a density in kg/km^2^ by

\begin{equation}
  C_{y_i}=\frac{1}{n_{y_i}} \sum\limits_{j=1}^{n_{y_i}} \frac{W_{y_i,j}}{D_{y_i,j}w_{y_i,j}}
  (\#eq:sweptareacpue)
\end{equation}

where
$W_{y_i,j}$ = catch weight (kg) for Pacific Cod in stratum $i$ for year $y$ and tow $j$,
$D_{y_i,j}$ = distance travelled (km) by tow $j$ in stratum $i$ for year $y$,
$w_{y_i,j}$ = net opening (km) by tow $j$ in stratum $i$ for year $y$, and
$n_{y_i}$ = number of tows in stratum $i$.

The variance of the survey biomass estimate $V_y$ for Pacific Cod in year $y$
was calculated in kg^2^ as follows:

\begin{equation}
  V_y=\sum_{i=1}^k\frac{\sigma_{y_i}^2A_i^2}{n_{y_i}}=\sum_{i=1}^kV_{y_i}
  (\#eq:sweptareavariance)
\end{equation}

where $\sigma_{y_i}^2$ is the variance of the CPUE in $kg^2/km^4$ for year $y$ in
stratum $i$, $V_{y_i}$ is the variance of Pacific Cod in stratum $i$ for year $y$,
and where $\sigma_{y_i}^2$ was obtained from bootstrapped samples (see below).

The CV for Pacific Cod for each year $y$ was calculated as follows:

\begin{equation}
  (CV)_y=\frac{{V_y}^{1/2}}{B_y}
  (\#eq:sweptareacv)
\end{equation}

where $(CV)_y$ is the CV for year $y$.

One thousand bootstrap replicates with replacement were constructed from the
survey data to estimate bias corrected 95% confidence intervals for each survey
year [@efron1982]. The resulting values are shown in Table
\@ref(tab:surv-canadian-table) and Figure \@ref(fig:surv-canadian).

```{r surv-canadian-table, results='asis'}
dplyr::filter(dat$survey_index, survey_abbrev %in%
  c("SYN QCS", "SYN WCVI", "SYN HS", "SYN WCHG", "OTHER HS MSA")) %>%
  dplyr::select(survey_abbrev, year, biomass, re, lowerci, upperci, num_sets, num_pos_sets) %>%
  dplyr::mutate(lowerci = round(lowerci/1000, 1), upperci = round(upperci/1000, 1),
    biomass = round(biomass/1000, 1), re = round(re, 2)) %>%
  dplyr::rename(`Survey abbrev.` = survey_abbrev, Year = year, Biomass = biomass,
    CV = re, `Lower CI` = lowerci, `Upper CI` = upperci, Sets = num_sets, `Positive sets` = num_pos_sets) %>%
  dplyr::arrange(`Survey abbrev.`, Year) %>%
  knitr::kable(caption = "Pacific Cod survey data for Canadian trawl surveys. Relative biomass and associated lower and upper confidence intervals (CI) are shown in metric tons (without accounting for survey catchability). Positive sets refers to the number of trawl sets that caught Pacific Cod.", booktabs = TRUE, linesep = "", 
    format = "pandoc")
```

```{r surv-canadian, fig.cap="Pacific Cod survey data for Canadian trawl surveys. Shown is relative biomass and associated lower and upper confidence intervals. Positive sets refers to the number of trawl sets that caught Pacific Cod."}
gfplot::tidy_survey_index(dat$survey_index,
  survey = c("SYN QCS", "SYN WCVI", "SYN HS", "SYN WCHG", "OTHER HS MSA")) %>%
  plot_survey_index()
```

```{r surv-canadian-table-write, results='asis'}
survout <- dplyr::filter(dat$survey_index, survey_abbrev %in%
  c("SYN QCS", "SYN WCVI", "SYN HS", "SYN WCHG", "OTHER HS MSA")) %>%
  dplyr::select(survey_abbrev, year, biomass, re, lowerci, upperci, num_sets, num_pos_sets) %>%
  dplyr::mutate(lowerci = round(lowerci/1000, 1), upperci = round(upperci/1000, 1),
    biomass = round(biomass/1000, 1), re = round(re, 2)) %>%
  dplyr::rename(`Survey abbrev.` = survey_abbrev, Year = year, Biomass = biomass,
    CV = re, `Lower CI` = lowerci, `Upper CI` = upperci, Sets = num_sets, `Positive sets` = num_pos_sets) %>%
  dplyr::arrange(`Survey abbrev.`, Year)
readr::write_csv(survout, here::here("data/generated/all_surveys.csv"))
```

\clearpage

## NMFS TRIENNIAL SURVEY (IN CANADIAN WATERS)

A relative abundance index was developed for Area 3CD from data from the
National Marine Fisheries Service (NMFS) Triennial survey operated off the
lower half of Vancouver Island. See Appendix A of @forrest2018 for complete details.

```{r tri-fig9, fig.cap="Biomass estimates for three series of Pacific Cod in the INPFC Vancouver region (total region, Canadian waters only, US waters only) with 95\\% error bars estimated from 1000 bootstraps."}
insert_paul_figure(9)
```

<!--
```{r tri-fig10, fig.cap="Proportion of tows with Pacific Cod by year for the Vancouver INPFC region (Canadian and US waters)."}
insert_paul_figure(10)
```
-->

\clearpage
