<!-- TODO: mention p and phi estimates, sigmas -->
<!-- TODO: show shapes that Tweedie can take -->
\clearpage

# COMMERCIAL CPUE STANDARDIZATION

We used the same approach for standardizing the historical (1956:1995) and modern (1996+) commercial CPUE indices as in the previous assessment [@forrest2020], with data added for 2018 and 2019.


```{r cpue-funcs}
source(here::here('R/cpue-functions.R'))
```

```{r cpue-params}
params <- list()
params$species_proper <- "Pacific Cod"
params$april1_year <- TRUE
params$area <- c("5[ABCD]+", "3[CD]+")
params$area_name <- c("5ABCD", "3CD")
params$skip_single_variable_models <- FALSE
```

```{r cpue-run-historic, message=FALSE, warning=FALSE, results='hide'}
params$era <- "historic"
source(here::here("R/cpue.R"))
dfleet_hist <- dfleet
gg_cpue_hist <- gg_cpue
cpue_pred_hist <- predictions
arith_cpue_hist <- arith_cpue
m_historic <- readRDS(here::here("data/generated/cpue-models-pcod-historic.rds"))
```

```{r cpue-run-modern, message=FALSE, warning=FALSE, results='hide'}
params$era <- "modern"
source(here::here("R/cpue.R"))
dfleet_modern <- dfleet
gg_cpue_modern <- gg_cpue
cpue_pred_modern <- predictions
arith_cpue_modern <- arith_cpue
m_modern <- readRDS(here::here("data/generated/cpue-models-pcod-modern.rds"))
```

```{r cpue-save}
readr::write_csv(cpue_pred_modern, here::here("data/generated/cpue-predictions-modern.csv"))
readr::write_csv(cpue_pred_hist, here::here("data/generated/cpue-predictions-historical.csv"))
```

```{r cpue-locality-map-5, fig.cap="DFO localities used in the 5ABCD modern CPUE standardization model.", fig.asp=0.9}
gfplot:::plot_dfo_localities(unique(dfleet_modern[[1]]$locality_code))
```

```{r cpue-locality-map-3, fig.cap="DFO localities used in the 3CD modern CPUE standardization model.", fig.asp=0.9}
gfplot:::plot_dfo_localities(unique(dfleet_modern[[2]]$locality_code))
```

```{r cpue-tweedie-ex, fig.asp=0.7, fig.cap="Example density functions for the Tweedie distribution. The symbol $\\phi$ (written as phi in this figure) represents the dispersion parameter, $p$ represents the power parameter, and $\\mu$ represents the mean. Note that the spike in density that is seen towards the left of the panels is at a value of 0 on the x axis."}
plot_tweedie_ex <- function(df, max = 15) {
  xx <- seq(0, max, length.out = 1000)
  out <- plyr::mdply(df, function(mu, power, phi) {
    data.frame(x = xx,
      y = tweedie::dtweedie(y = xx, mu = mu, power = power, phi = phi))
  }) %>%
    mutate(phi = paste("phi =", phi)) %>%
    mutate(power = paste("p =", power)) %>%
    mutate(mu = paste("μ =", mu))

  ggplot(out, aes(x, y, colour = mu)) +
    geom_line() +
    facet_grid(power~phi, scales = "free") +
    gfplot::theme_pbs() +
    labs(colour = "μ") +
    xlab("Value") + ylab("Density") +
    coord_cartesian(expand = FALSE, xlim = c(-0.2, max(out$x))) +
    scale_colour_brewer(palette = "Dark2") +
    scale_fill_brewer(palette = "Dark2")
}

df <- expand.grid(power = c(1.2, 1.6, 1.8), mu = c(1, 3, 6), phi = c(0.5, 1, 2))
plot_tweedie_ex(df)
```

```{r cpue-catch-effort-ts, fig.cap="Raw time series of Pacific Cod catch and total hours trawled (regardless of species caught). Data prior to 1996 is shown separately from data after 1996.", fig.asp=1.1}
g1 <- make_catch_effort_ts_plot(dfleet_hist)  +
  ggtitle("1956-1995 data")
#RF added the _modern function to accommodate effort field
g2 <- make_catch_effort_ts_plot_modern(dfleet_modern) +
  ggtitle("1996+ data")
cowplot::plot_grid(g1, g2, ncol = 1)
```

```{r, cpue-depth-hists, fig.asp=0.8, fig.cap="The depth distribution for fishing trips (top row) and fishing trawl events (bottom row) that caught Pacific Cod or did not catch Pacific Cod."}
g1 <- gg_cpue_modern$depth + ylab("Fishing event count") + xlab("Depth") +
  labs(fill = "Fishing event\ncaught\nPacific Cod") +
  theme(legend.position = c(0.95, 0.95), legend.background = element_rect(fill = "white"),
    legend.justification = c(1, 1)) +
  ggtitle("1996+ data") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2")

g2 <- gg_cpue_hist$depth + ylab("Trip count") + xlab("Depth") +
  labs(fill = "Trip\ncaught\nPacific Cod") +
  theme(legend.position = c(0.95, 0.95), legend.background = element_rect(fill = "white"),
    legend.justification = c(1, 1)) +
  ggtitle("1956-1995 data")  +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2")

cowplot::plot_grid(g2, g1, ncol = 1)
```

```{r cpue-bubble-plots-hist-3CD, fig.asp=1.35, fig.cap="Distribution of predictors in CPUE standardization models for 1956--1995 3CD dataset. Area of outermost circles represents the number of trip-locality combinations for that predictor value and year combination. Area and shading of innermost circles represents the number of trip-locality combinations for that predictor value and year combination that caught Pacific Cod."}
dfleet_hist %>%
  make_bubble_dat(measure.vars = c("month", "locality", "depth")) %>%
  filter(area == "3CD") %>%
  make_facet_bubble_plot(group = "trips") +
  ggtitle("1956-1995 3CD")
```

(ref:caption-cpue-bubble-plots-hist-5ABCD) Same as Figure \@ref(fig:cpue-bubble-plots-hist-3CD) but for 5ABCD.
(ref:caption-cpue-bubble-plots-modern-3CD) Same as Figure \@ref(fig:cpue-bubble-plots-hist-3CD) but for 1996--2017 3CD.
(ref:caption-cpue-bubble-plots-modern-5ABCD) Same as Figure \@ref(fig:cpue-bubble-plots-hist-3CD) but for 1996--2017 5ABCD.

```{r cpue-bubble-plots-hist-5ABCD, fig.asp=1.35, fig.cap="(ref:caption-cpue-bubble-plots-hist-5ABCD)"}
dfleet_hist %>%
  make_bubble_dat(measure.vars = c("month", "locality", "depth")) %>%
  filter(area == "5ABCD") %>%
  make_facet_bubble_plot(group = "trips") +
  ggtitle("1956-1995 5ABCD")
```

```{r cpue-bubble-plots-modern-3CD, fig.asp=1.4, fig.width=9, fig.cap="(ref:caption-cpue-bubble-plots-modern-3CD)"}
dfleet_modern %>% make_bubble_dat() %>%
  filter(area == "3CD") %>%
  make_facet_bubble_plot() +
  ggtitle("1996+ 3CD")
```

```{r cpue-bubble-plots-modern-5ABCD, fig.asp=1.4, fig.width=9, fig.cap="(ref:caption-cpue-bubble-plots-modern-5ABCD)"}
dfleet_modern %>% make_bubble_dat() %>%
  filter(area == "5ABCD") %>%
  make_facet_bubble_plot() +
  ggtitle("1996+ 5ABCD")
```

(ref:caption-cpue-quantile-residuals) Histograms of randomized quantile residuals [@dunn1996] for the CPUE GLMM standardization models. The histograms illustrate the actual density distribution of 10,000 randomly selected randomized quantile residuals. The dashed lines show the probability density for a normal distribution with the same standard deviation.

```{r cpue-quantile-residuals, fig.asp=0.8, fig.cap="(ref:caption-cpue-quantile-residuals)"}
stopifnot(length(m_historic) == 12L)
stopifnot(length(m_modern) == 16L)
qr1 <- qres_tweedie(m_historic[[6]], "cpue")
gqr1 <- plot_qres_histogram(qr1) + ggtitle(paste("Historical", params$area_name[1]))
qr2 <- qres_tweedie(m_historic[[12]], "cpue")
gqr2 <- plot_qres_histogram(qr2) + ggtitle(paste("Historical", params$area_name[2]))
qr3 <- qres_tweedie(m_modern[[8]], "cpue")
gqr3 <- plot_qres_histogram(qr3) + ggtitle(paste("Modern", params$area_name[1]))
qr4 <- qres_tweedie(m_modern[[16]], "cpue")
gqr4 <- plot_qres_histogram(qr4) + ggtitle(paste("Modern", params$area_name[2]))
cowplot::plot_grid(gqr2, gqr1, gqr4, gqr3, ncol = 2)
```

```{r cpue-pars, results='asis'}
get_cpue_pars <- function(obj, name = "") {
  re <- broom.mixed::tidy(obj, effects = "ran_pars")
  re$group <- gsub("_", "-", re$group)
  re <- tibble(Model = name, Parameter = paste(re$group, "SD"),
    Estimate = round(re$estimate, 2))
  p <- round(stats::plogis(obj$fit$par[["thetaf"]]) + 1, 2)
  phi <- round(exp(obj$fit$par[["betad"]]), 2)
  bind_rows(re,
    tibble(Model = name, Parameter = c("$p$", "$\\phi$"), Estimate = c(p, phi)))
}
pars <- list()
pars[[1]] <- get_cpue_pars(m_historic[[12]], "Historical 3CD")
pars[[2]] <- get_cpue_pars(m_historic[[6]], "Historical 5ABCD")
pars[[3]] <- get_cpue_pars(m_modern[[16]], "Modern 3CD")
pars[[4]] <- get_cpue_pars(m_modern[[8]], "Modern 5ABCD")
bind_rows(pars) %>%
  knitr::kable(caption = "Random effect standard deviation (SD) and Tweedie observation model power ($p$) and dispersion ($\\phi$) parameter estimates.", booktabs = TRUE, linesep = "", escape = FALSE, format = "pandoc")
```


```{r cpue-index-ts-hist, fig.asp=1.15, fig.cap="Commercial trawl CPUE standardization models. Throughout, the black line and shaded region indicate a CPUE index with only a year predictor. The coloured line and shaded ribbons indicate indices that have been standardized by one or more predictors. The first three rows illustrate standardization models that include a single predictor listed on the right. The second last row illustrates a standardization model that includes all the predictors in one model. The last row illustrates a standardization model that includes all the predictors plus locality-by-year (space-time) random effects. Locality and locality-vessel interactions are fit as random effects and all other variables are fit as fixed effects."}
make_cpue_ts_dat(cpue_pred_hist) %>% make_cpue_ts_plot() +
  ggtitle("1956-1995 CPUE") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2")
```

(ref:caption-cpue-index-ts-modern) Same as Figure \@ref(fig:cpue-index-ts-hist) but for the 1996 to 2017 data. Locality, vessel, and locality-vessel interactions are fit as random effects and all other variables are fit as fixed effects.

```{r cpue-index-ts-modern, fig.asp=1.55, fig.cap="(ref:caption-cpue-index-ts-modern)", out.width="5.2in", fig.width=6.5}
make_cpue_ts_dat(cpue_pred_modern) %>% make_cpue_ts_plot() +
  ggtitle("1996+ CPUE") +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2")
```

```{r cpue-int-test-plot, fig.asp=0.85, fig.cap="A comparison of CPUE timeseries standardized with a model that does not include locality-year (space-time) random effects (black/grey) and a model that does include the locality-year random effects (coloured)."}
g1 <- make_cpue_ts_dat_noint(cpue_pred_hist) %>% make_cpue_ts_plot_noint() +
  ggtitle("1956-1995 CPUE")
g2 <- make_cpue_ts_dat_noint(cpue_pred_modern) %>% make_cpue_ts_plot_noint() +
  ggtitle("1996+ CPUE")
cowplot::plot_grid(g1, g2, ncol = 1)
```

```{r cpue-coef-plot1, fig.asp=1.3, echo=FALSE, fig.cap="Fixed effect coefficients for historical commercial CPUE standardization model. Dots and thick and thin line segments represent means and 50\\% and 95\\% Wald confidence intervals."}
toplot <- c(6, 12)
p <- list()
for (i in seq_along(params$area_name)) {
  p[[i]] <- make_fe_plots(m_historic[[toplot[i]]]) + ggtitle(params$area_name[i])
}
cowplot::plot_grid(p[[2]], p[[1]], ncol = 1)
```

```{r cpue-coef-plot2, fig.asp=1, echo=FALSE, fig.cap="Locality random effects for the historical commercial CPUE standardization model."}
p <- list()
for (i in seq_along(params$area_name)) {
   p[[i]] <- make_re_plots(m_historic[[toplot[i]]], re_names = "locality") +
    ggtitle(params$area_name[i]) + xlab("Random intercept value\n(log space)")
}
cowplot::plot_grid(p[[2]], p[[1]], ncol = 2)
```

```{r cpue-coef-plot3, fig.asp=1.35, echo=FALSE, fig.cap="Locality-by-year (space-time) random effects for the historical commercial CPUE standardization model.", fig.width=10.5}
p <- list()
for (i in seq_along(params$area_name)) {
  p[[i]] <- make_year_locality_plots(m_historic[[toplot[i]]]) + ggtitle(params$area_name[i])
}
cowplot::plot_grid(p[[2]], p[[1]], ncol = 1)
```

```{r cpue-coef-plot1-modern, fig.asp=1.2, echo=FALSE, fig.cap="Fixed effect coefficients for modern commercial CPUE standardization model. Dots and thick and thin line segments represent means and 50\\% and 95\\% Wald confidence intervals."}
toplot <- c(8, 16)
p <- list()
for (i in seq_along(params$area_name)) {
  p[[i]] <- make_fe_plots(m_modern[[toplot[i]]]) + ggtitle(params$area_name[i])
}
cowplot::plot_grid(p[[2]], p[[1]], ncol = 2)
```

```{r cpue-coef-plot2-modern, fig.asp=0.8, echo=FALSE, fig.cap="Locality and vessel random effects for the modern commercial CPUE standardization model."}
p <- list()
for (i in seq_along(params$area_name)) {
   p[[i]] <- make_re_plots(m_modern[[c(8, 16)[i]]], re_names = c("locality", "vessel")) +
    ggtitle(params$area_name[i])
}
cowplot::plot_grid(p[[2]], p[[1]], ncol = 2)
```

```{r cpue-coef-plot3-modern, fig.asp=1.35, echo=FALSE, fig.cap="Locality-by-year (space-time) random effects for the modern commercial CPUE standardization model."}
p <- list()
for (i in seq_along(params$area_name)) {
  p[[i]] <- make_year_locality_plots(m_modern[[toplot[i]]]) + ggtitle(params$area_name[i])
}
cowplot::plot_grid(p[[2]], p[[1]], ncol = 1)
```

```{r cpue-re-int-ts, fig.cap="Locality-specific CPUE index trends for a standardization model that allows for locality-year (space-time) interactions. The coloured lines indicate the locality-specific estimates with all other predictors set to their base levels. The black line and shaded ribbon indicate the overall average annual CPUE.", fig.asp=0.8}
if (!file.exists(here::here("data/generated/cpue-re-preds.rda"))) {
  stopifnot(length(m_modern) == 16L)
  g1 <- plot_cpue_int_res(m_modern[[8]], fleet = dfleet_modern[[1]],
    index_data = cpue_pred_modern,
    era = "modern") + ggtitle("1996+ 5ABCD")

  g2 <- plot_cpue_int_res(m_modern[[16]], fleet = dfleet_modern[[2]],
    index_data = cpue_pred_modern,
    era = "modern") + ggtitle("1996+ 3CD")

  stopifnot(length(m_historic) == 12L)
  g3 <- plot_cpue_int_res(m_historic[[6]], fleet = dfleet_hist[[1]],
    index_data = cpue_pred_hist,
    era = "historical")+ ggtitle("1956-1995 5ABCD")

  g4 <- plot_cpue_int_res(m_historic[[12]], fleet = dfleet_hist[[2]],
    index_data = cpue_pred_hist,
    era = "historical")+ ggtitle("1956-1995 3CD")

  save(g1, g2, g3, g4, file = here::here("data/generated/cpue-re-preds.rda"))
} else {
  load(here::here("data/generated/cpue-re-preds.rda"))
}
cowplot::plot_grid(g4, g3, g2, g1, ncol = 2)
```


```{r cpue-re-no-int-ts, fig.cap="Locality-specific CPUE index trends for a standardization model that does not allow for locality-year (space-time) interactions. The coloured lines indicate the locality-specific estimates with all other predictors set to their base levels. The black line and shaded ribbon indicate the overall average annual CPUE.", fig.asp=0.8}
if (!file.exists(here::here("data/generated/cpue-re-preds-noint.rda"))) {
  g1 <- plot_cpue_int_res(m_modern[[7]], fleet = dfleet_modern[[1]],
    index_data = cpue_pred_modern,
    the_formula_version = "Full standardization minus interactions",
    era = "modern") + ggtitle("1996+ 5ABCD")

  g2 <- plot_cpue_int_res(m_modern[[15]], fleet = dfleet_modern[[2]],
    index_data = cpue_pred_modern,
    the_formula_version = "Full standardization minus interactions",
    era = "modern") + ggtitle("1996+ 3CD")

  g3 <- plot_cpue_int_res(m_historic[[5]], fleet = dfleet_hist[[1]],
    index_data = cpue_pred_hist,
    the_formula_version = "Full standardization minus interactions",
    era = "historical")+ ggtitle("1956-1995 5ABCD")

  g4 <- plot_cpue_int_res(m_historic[[11]], fleet = dfleet_hist[[2]],
    index_data = cpue_pred_hist,
    the_formula_version = "Full standardization minus interactions",
    era = "historical")+ ggtitle("1956-1995 3CD")
  save(g1, g2, g3, g4, file = here::here("data/generated/cpue-re-preds-noint.rda"))
} else {
  load(here::here("data/generated/cpue-re-preds-noint.rda"))
}
cowplot::plot_grid(g4, g3, g2, g1, ncol = 2)
```

```{r cpue-sim-test-tweedie-glmm, message=FALSE, warning=FALSE, results='hide'}
set.seed(99)
N <- 12
nyrs <- 20
locs <- LETTERS[seq_len(N)]
loc_effects <- rnorm(N, 0, 0.3)
yr_effects <- as.numeric(arima.sim(n = nyrs, list(ar = 0.3), sd = 1, mean = 2))
obs_per_yr_loc <- 10
tweedie_p <- 1.6
tweedie_phi <- 5

x <- data.frame(loc = rep(locs, each = nyrs * obs_per_yr_loc),
  loc_ef = rep(loc_effects, each = nyrs * obs_per_yr_loc))
x <- mutate(x, yr = rep(seq_len(nyrs), N * obs_per_yr_loc),
  yr_ef = rep(yr_effects, N * obs_per_yr_loc))
x <- mutate(x, mu = yr_ef + loc_ef)
x <- mutate(x, yr_x_loc = paste(yr, loc))
x <- mutate(x, y = tweedie::rtweedie(length(mu),
  mu = exp(mu), power = tweedie_p, phi = tweedie_phi))
# ggplot(x, aes(yr, y)) + geom_point() + geom_line(aes(x = yr, y = exp(yr_ef)))

yr_loc_int <- expand.grid(yr = unique(x$yr), loc = unique(x$loc))
yr_loc_int <- mutate(yr_loc_int, yr_x_loc = paste(yr, loc))
yr_loc_int <- mutate(yr_loc_int, yr_x_loc_ef = rnorm(nrow(yr_loc_int), 0, 0.5))

x <- left_join(x, yr_loc_int, by = c("loc", "yr", "yr_x_loc"))

x <- mutate(x, mu_w_int = yr_ef + loc_ef + yr_x_loc_ef)
x <- mutate(x, y_w_int =
    tweedie::rtweedie(length(mu_w_int),
      mu = exp(mu_w_int), power = tweedie_p, phi = tweedie_phi))
# ggplot(x, aes(yr, y_w_int)) + geom_point() + geom_line(aes(x = yr, y = exp(yr_ef)))

d1 <- x %>% sample_frac(1) %>%
  reshape2::melt(id.vars = c("loc", "yr", "yr_ef"), measure.vars = c("y", "y_w_int"))
# d1 %>% ggplot(aes(yr, value)) + geom_point(alpha = 0.7, pch = 21) +
#   geom_line(aes(x = yr, y = exp(yr_ef))) +
#   facet_wrap(~variable)

d1 <- mutate(d1, year_factor = as.factor(yr), cpue = value)
d1 <- mutate(d1, yr_x_loc = paste(yr, loc))

invisible(capture.output({
  m_int <- plyr::dlply(d1, "variable", function(xx)
    gfplot::fit_cpue_index_glmmtmb(xx, formula = cpue ~ 0 + year_factor + (1|loc) + (1|yr_x_loc)))
  m_no_int <- plyr::dlply(d1, "variable", function(xx)
    gfplot::fit_cpue_index_glmmtmb(xx, formula = cpue ~ 0 + year_factor + (1|loc)))
}))

x1 <- plyr::ldply(m_int, function(xx) gfplot::predict_cpue_index_tweedie(xx)) %>%
  mutate(model = "Space-time interactions")
x2 <- plyr::ldply(m_no_int, function(xx) gfplot::predict_cpue_index_tweedie(xx)) %>%
  mutate(model = "No space-time interactions")
pp <- bind_rows(x1, x2)

orig_dat <- select(x, yr, yr_ef) %>% unique() %>%
  mutate(yr_ef = yr_ef - mean(yr_ef)) %>%
  rename(year = yr)
```

```{r cpue-sim-test-tweedie-glmm-plot, fig.cap="An example simulation illustrating the effect of modelling or not modelling space-time interactions as random effects in a CPUE index standardization model. Left panel shows a scenario where the data were generated with the same trend for all localities in space. Right panel shows a scenario where the data were generated with space-time interactions. The green and orange lines and shaded regions represent estimated CPUE indices from models that allow for space-time interactions or do not allow for space-time interactions along with 95\\% confidence intervals. The dashed black line indicates the true mean CPUE for each year. All model and data combinations have correct 95\\% coverage except for the no-space-time-interactions model fitted to data that does have space-time interactions, which has 55\\% coverage. Note that the confidence intervals in the left panel are completely overlapping.", fig.asp=0.45}
pp <- left_join(pp, orig_dat, by = "year") %>%
  mutate(est_link = est_link - mean(est_link)) %>%
  ungroup() %>%
  mutate(variable = gsub("^y$", "Data have no space-time interactions", variable)) %>%
  mutate(variable = gsub("^y_w_int$", "Data have space-time interactions", variable)) %>%
  mutate(model = forcats::fct_rev(model))

gg <- pp %>% group_by(model, variable) %>%
  ungroup() %>%
  ggplot() +
  geom_ribbon(aes(x = year, ymin = exp(est_link - 1.96 * se_link),
    ymax = exp(est_link + 1.96 * se_link), fill = model), alpha = 0.4) +
  geom_line(aes(x = year, y = exp(est_link), colour = model), lwd = 0.8) +
  facet_grid(~variable) +
  geom_line(data = orig_dat, aes(x = year, y = exp(yr_ef)), lwd = 0.9, col = "grey20", lty = 2) +
  labs(fill = "Model", colour = "Model", x = "Year", y = "CPUE") +
  gfplot::theme_pbs() +
  theme(legend.position = c(0.02, 0.97), legend.justification = c(0, 1))  +
  scale_colour_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2")
print(gg)
```

```{r cpue-sim-save}
ggplot2::ggsave(here::here("presentations/figures/cpue-sim.svg"), plot = gg, 
  width = 8, height = 4)
```

```{r cpue-sim-test-tweedie-glmm-table, results='asis'}
# group_by(pp, variable, model) %>%
#   rename(data = variable) %>%
#   summarise(coverage =
#     sum(yr_ef < est_link + 1.96 * se_link & yr_ef > est_link - 1.96 * se_link) / n()) %>%
#   knitr::kable(caption = "TODO", booktabs = TRUE, linesep = "")
```

\clearpage
